\bf Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-14 appendix.qmd
Fixed the reference

Following the process in @xia2023 again using the Human Peripheral Blood Mononuclear Cells (PBMC) data. Note that @xia2023 uses a different subset from the PBMC dataset used by @chen2023, which contains $31,021$ cells including cell type labels, and the gene expression levels were in the unit of log-transformed UMI count per $10,000$. They focused on three sequencing methods (inDrops, DropSeq, and SeqWell) and four common cell types Cytotoxic T cell, CD4+T cell, CD14+ Monocyte, and B cell.

>>>>

Following the process in @xia2023 again using the Human Peripheral Blood Mononuclear Cells (PBMC) data. Note that @xia2023 uses a different subset from the PBMC dataset used by @chen2024, which contains $31,021$ cells including cell type labels, and the gene expression levels were in the unit of log-transformed UMI count per $10,000$. They focused on three sequencing methods (inDrops, DropSeq, and SeqWell) and four common cell types Cytotoxic T cell, CD4+T cell, CD14+ Monocyte, and B cell.

### 2025-05-14 appendix.tex
Fixed the reference

Following the process in \citet{xia2023} again using the Human
Peripheral Blood Mononuclear Cells (PBMC) data. Note that
\citet{xia2023} uses a different subset from the PBMC dataset used by
\citet{chen2023}, which contains \(31,021\) cells including cell type
labels, and the gene expression levels were in the unit of
log-transformed UMI count per \(10,000\). They focused on three
sequencing methods (inDrops, DropSeq, and SeqWell) and four common cell
types Cytotoxic T cell, CD4+T cell, CD14+ Monocyte, and B cell.

>>>>

Following the process in \citet{xia2023} again using the Human
Peripheral Blood Mononuclear Cells (PBMC) data. Note that
\citet{xia2023} uses a different subset from the PBMC dataset used by
\citet{chen2024}, which contains \(31,021\) cells including cell type
labels, and the gene expression levels were in the unit of
log-transformed UMI count per \(10,000\). They focused on three
sequencing methods (inDrops, DropSeq, and SeqWell) and four common cell
types Cytotoxic T cell, CD4+T cell, CD14+ Monocyte, and B cell.
